A Survey of Physical Design Techniques of Information Systems

### 2010-07-12 trunk/cs848-db/Paper.tex

@@

Since XPath query processing is expensive, materialized views come in handy in XML databases. Balmin et al.~\cite{balmin2004framework} propose a framework for
using XPath materialized views for XML query processing. (TALK ABOUT IT MORE)

>>>>

Besides indexing the actual nodes, path indexing is also common in XML databases since usually queries search for a specific path. This is done by clustering
together all the IDs of nodes on a given path, and creating an index for them~\cite{milo1999index, arion2008path}.

@@

The main idea behind using materialized views is to rewrite queries using these views so that they run more efficiently. Given the semi-structured nature of
XML data, and the expressiveness of most XML querying languages, view selection for optimization becomes a more complicated
problem~\cite{tang2009materialized}. Therefore, the choice of which views to materialize becomes more complicated in XML database. That is, of course, besides
the difficulty of selecting which views to use for rewriting. However, this problem is not within the scope this survey. Since XPath query processing is
expensive, materialized views come in handy in XML databases. Balmin et al.~\cite{balmin2004framework} propose a framework for
using XPath materialized views for XML query processing. (TALK ABOUT IT MORE)

\subsubsection{Partitioning}
In XML-enabled databases, inlining during the shredding of the data such that children nodes that occur only once are stored with the parent node produces
better partitioned data~\cite{tatarinov2002storing}. Inlining shreds a document into sets of tables according to the document schema which leads to better
performance because queries tend to access less data. Such inlining is similar to horizontal partitioning~\cite{ramanath2003searching}.
